title: "Sentiment Analysis on Happy Moments"
author: "Your Name"
output: html_document
---

## Introduction

This analysis aims to explore the HappyDB dataset to understand what makes people happy. We will focus on the most frequently used words to express happiness among different genders.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(DT)
library(wordcloud2)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 


# call function lib
source("lib/analysis_functions.R")
```

```{r load data, warning=FALSE, message=FALSE}
hm_data <- read_csv("/Users/lizan/Documents/GitHub/52243project1R/output/processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```

```{r combining data, warning=FALSE, message=FALSE}
# Combine both the data sets and keep the required columns for analysis
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```


### calculate word count using function


```{r setup, include=FALSE}
my_word_count <- calculate_word_count(hm_data, "text")


```


# Create a bag of words using the text data

```{r combining data, warning=FALSE, message=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)

word_count <- bag_of_words %>%
  count(gender, word, sort = TRUE)
```


# visulize the result
```{r combining data, warning=FALSE, message=FALSE}
# Filter top 10 most frequent words for each gender
top_words <- word_count %>%
  group_by(gender) %>%
  top_n(10, wt = n)

# Visualize the result
ggplot(top_words, aes(x = reorder(word, n), y = n, fill = gender)) +
  geom_col() +
  coord_flip() +
  labs(title = "Most Frequently Used Words to Express Happiness Among Different Genders",
       x = "Words",
       y = "Frequency") +
  facet_wrap(~gender)


# Create separate data frames for each gender
male_words <- filter(top_words, gender == "m")
female_words <- filter(top_words, gender == "f")

```

```{r}
library(tidytext)

head(sentiments)


```


### Sentiment Score by Gender

use the `bing` lexicon to calculate the sentiment score for each word and then aggregate them by gender.

```{r sentiment-score}
# Load the tidytext package
library(tidytext)

# Calculate sentiment score
sentiment_score <- bag_of_words %>%
  inner_join(sentiments, by = "word") %>%
  count(gender, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment_score = positive - negative)

# Visualize the sentiment score by gender
ggplot(sentiment_score, aes(x = gender, y = sentiment_score, fill = gender)) +
  geom_col() +
  labs(title = "Sentiment Score by Gender",
       x = "Gender",
       y = "Sentiment Score")
```


```{r}

library(igraph)
library(ggraph)
library(tidyr)  

# Create bigrams
bigrams <- hm_data %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

# Count and filter to get top 50 bigrams
bigram_count <- bigrams %>%
  count(bigram, sort = TRUE) %>%
  head(100)

# Remove rows where bigram is NA
bigram_count <- bigram_count %>%
  drop_na(bigram)

# Create a network graph
bigram_network <- bigram_count %>%
  separate(bigram, c("word1", "word2"), sep = " ", remove = FALSE) %>%
  drop_na(word1, word2) %>%
  graph_from_data_frame()

# Visualize the network
ggraph(bigram_network, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE) +
  geom_node_point(color = "blue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```


```{r}
# 首先确保hm_data和bag_of_words都有一个共同的列（例如，'wid'）用于连接。
# 然后执行内连接。
combined_data <- inner_join(bag_of_words, hm_data, by = "wid")
```

```{r}
# 查看combined_data的列
colnames(combined_data)

```


```{r}
# 重命名列以去除.x和.y后缀
combined_data <- combined_data %>%
  rename(
    gender = gender.x,
    marital = marital.x
  )

# 现在，我们可以按性别和婚姻状况对单词进行计数。
word_count_gender_marital <- combined_data %>%
  count(gender, marital, word, sort = TRUE) %>%
  group_by(gender, marital) %>%
  top_n(5, wt = n)

# 可视化结果
ggplot(word_count_gender_marital, aes(x = reorder(word, n), y = n, fill = marital)) +
  geom_col() +
  coord_flip() +
  labs(title = "Top 5 Words Used to Express Happiness by Gender and Marital Status",
       x = "Words",
       y = "Frequency") +
  facet_grid(marital ~ gender)


```
```{r}
# 现在，我们可以按性别和婚姻状况对单词进行计数。
word_count_gender_marital <- combined_data %>%
  count(gender, marital, word, sort = TRUE) %>%
  group_by(gender, marital) %>%
  mutate(total = sum(n)) %>%
  top_n(5, wt = n) %>%
  ungroup() %>%
  mutate(percentage = n / total * 100)

# 可视化结果
ggplot(word_count_gender_marital, aes(x = reorder(word, percentage), y = percentage, fill = marital)) +
  geom_col() +
  coord_flip() +
  labs(title = "Top 5 Words Used to Express Happiness by Gender and Marital Status",
       x = "Words",
       y = "Percentage (%)") +
```


```{r}

```


```{r}
```


```{r}
facet_grid(marital ~ gender)